NTM CT Scoring - Initial Agreement

### 2023-05-17 Stacey Martiniano/ntm_agreement.qmd
Update ntm_agreement.qmd
NTM duplicates done

      ggtitle(f)

@@

    arrange(feature,n,location)

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

>>>>

      custom_colors

@@

    pivot_wider(names_from = n, values_from = AF:JW) %>%

@@

  af = kappa2(df[,c("AF_1","AF_2")])
  dl = kappa2(df[,c("DL_1","DL_2")])
  jw = kappa2(df[,c("JW_1","JW_2")])

@@

    select(feature, location, AF_1:JW_2) %>%
    pivot_longer(AF_1:JW_2) %>%

@@

  cat("Cohen's Kappa for AF"," was ",round(af$value,3)," (p = ",

@@

  cat("Cohen's Kappa for DL"," was ",round(dl$value,3)," (p = ",

@@

  cat("Cohen's Kappa for JW"," was ",round(jw$value,3)," (p = ",

@@

    t = data.frame(df[df$feature == f,c("AF_1","AF_2","DL_1","DL_2","JW_1","JW_2")])

@@

    af = kappa2(t[,c("AF_1","AF_2")])
    dl = kappa2(t[,c("DL_1","DL_2")])
    jw = kappa2(t[,c("JW_1","JW_2")])

@@

      select(location, AF_1:JW_2) %>%
      pivot_longer(AF_1:JW_2) %>%

@@

      cat("Agreement within AF",f,"was perfect.")

@@

      cat("Cohen's Kappa for AF",f," was ",round(af$value,3)," (p = ",

@@

      cat("Agreement within DL",f,"was perfect.")

@@

      cat("Cohen's Kappa for DL",f," was ",round(dl$value,3)," (p = ",

@@

      cat("Agreement within JW in",f,"was perfect.")

@@

      cat("Cohen's Kappa for JW",f," was ",round(jw$value,3)," (p = ",

@@

```{r results='asis',warning=FALSE}
compare(df = dup_df,scan_num = 1062761)
```

```{r results='asis',warning=FALSE}
compare(df = dup_df,scan_num = 1151991)
```

```{r results='asis',warning=FALSE}
compare(df = dup_df,scan_num = 1340551)
```

```{r results='asis',warning=FALSE}
compare(df = dup_df,scan_num = 1419420)
```

```{r results='asis',warning=FALSE}
compare(df = dup_df,scan_num = 1468121)
```
